Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-19 tex/paper1/paper1.tex
added in more references for power laws in other solar phenomena

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions (Figure
\ref{fig:fit171193}), and compared to decide which model best
describes the data. A Bayesian probability based parameter estimation
and model fitting is implemented.  This approach was chosen for its
flexibility and consistent error estimation properties
\citep{2013ApJ...769...89I}.  The details of the model fitting process
are described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
restricted by permitting $\beta$ to vary in the range $0.1-10$ mHz
only.  This restriction, which is imposed in the fitting process (see
Section \ref{sec:app:ind}), arises from the observations of
significant wavelet power in the period rangs 200 - 600 seconds as
found by \cite{2003ApJ...595L..63D}.

@@

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $M_{1}$ and $M_{2}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all {\bf similar} parts of the solar
atmosphere {\bf , that is quiet Sun, moss, loop footpoints and above
  sunspots}.  Further, \cite{2014AA...563A...8A} show that a
\PL\ \PS\ is present in time-series of coronal active region and quiet
Sun emission over the frequency range 0.01 - 1 mHz, overlapping with
the frequency studied in this paper.

{\bf \PL\ \PS\ have been observed in other solar phenomena.  Recently,
\citet{gupta2014} showed \PL\ \PS\ in coronal plumes extending over
}

We hypothesize that the \PL\ \PS\ in the coronal 171\AA\ and
193\AA\ emission is due to the sum of a distribution of a large number
of events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.

>>>>

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions (Figure
\ref{fig:fit171193}), and compared to decide which model best
describes the data. A Bayesian probability based parameter estimation
and model fitting is implemented.  This approach was chosen for its
flexibility and consistent error estimation properties
\citep{2013ApJ...769...89I}.  The details of the model fitting process
are described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
restricted by permitting $\beta$ to vary in the range $0.1-10$ mHz
only.  This restriction, which is imposed in the fitting process (see
Section \ref{sec:app:ind}), arises from the observations of
significant wavelet power in the period range 200 - 600 seconds as
found by \cite{2003ApJ...595L..63D}.

@@

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
{\bf Power-law \PS\ have been
  observed in other solar phenomena.  As was mentioned above,
  \cite{2014AA...563A...8A} observe power laws in the integrated
  emission of small portions of active regions and the quiet Sun as
  seen in the 19.5 nm passband images from EIT over the frequency
  range 0.01 - 1 mHz. Also, \citet{gupta2014} showed \PL\ \PA\ in the
  intensity at six single points in AIA 171 coronal plumes extending
  over the frequency range $0.3\rightarrow 4.0$ mHz.  Lower in the
  solar atmosphere, \cite{2008ApJ...683L.207R} show the presence of
  \PL\ Fourier \PA, in the range 7-20 mHz, in the Doppler velocity of
  the chromospheric Ca II 854.2 nm line as observed by the
  Interferometric Bidimensional Spectrometer (IBIS).  Further out in
  the solar atmosphere at 2.1 $R_{sun}$, \cite{2008ApJ...677L.137B}
  show the presence of \PL\ \PA\ in Ultraviolet Coronagraph
  Spectrometer observations of the intensity of Lyman-$\alpha$ in the
  frequency range $2.6\times10^{-6}\rightarrow1.3\times10^{-4}$ Hz.}

The first contribution to both models $M_{1}$ and $M_{2}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all {\bf similar} parts of the solar
atmosphere {\bf , that is quiet Sun, moss, loop footpoints and above
  sunspots}.  Further, \cite{2014AA...563A...8A} show that a
\PL\ \PS\ is present in time-series of coronal active region and quiet
Sun emission over the frequency range 0.01 - 1 mHz, overlapping with
the frequency studied in this paper.  We hypothesize that the
\PL\ \PS\ in the coronal 171\AA\ and 193\AA\ emission is due to the
sum of a distribution of a large number of events having different
amounts of emission.  \cite{2011soca.book.....A} describes how a
\PL\ \PS\ may obtained from such a distribution, and that argument is
outlined below.
